Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-23 doc/manuscript/ESSDmanuscript.Rmd
switch to reading record_of_changes direct from ForC repo
previously, was reading a copy manually added to this repo. This change simplifies/ ensures we have the latest version.

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE}
#"figures_tables/record_of_changes.csv" is copied over from the table located at  https://github.com/forc-db/ForC/blob/master/database_management_records/record_of_changes.csv, and I deleted the date field.

record_of_changes <- read.csv("figures_tables/record_of_changes.csv")
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")

>>>>

```{r table_ForCchanges, eval = TRUE, echo=FALSE, warning=FALSE}
library (readr)
urlfile="https://raw.githubusercontent.com/forc-db/ForC/master/database_management_records/record_of_changes.csv"
record_of_changes<-read_csv(url(urlfile))
names(record_of_changes) <- stringr::str_replace_all(names(record_of_changes), "\\.", " ")
record_of_changes <- record_of_changes[c(1:5)] #include all fields but date of change
record_of_changes[is.na(record_of_changes)]<- "" #replace NAs with blanks

### 2021-06-23 doc/manuscript/ESSDmanuscript.tex
switch to reading record_of_changes direct from ForC repo
previously, was reading a copy manually added to this repo. This change simplifies/ ensures we have the latest version.

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Use} & \textbf{Required}\\
\hline
Sites &  &  &  & \\
\hline
Measuremennts & variable.name & - & link to variable info in ForC\_variables table & y\\
\hline
 & mean & Value & (direct) & y\\
\hline
 & mean.in.original.units & Value in Common Units & (direct) & y\\
\hline
 & original.units & Common Unit & (direct) & y\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI &  &  & y\\
\hline
 &  &  &  & \\
\hline
 & data.location.within.source &  & confirm that data weren't digitized, facilitate finding data in original publication & y\\
\hline
PFT & description &  &  & \\
\hline
variables & units &  &  & y\\
\hline
Citations & (several fields) &  &  & \\
\hline
\end{tabu}
\end{table}

@@

@@

\caption{\label{tab:table_ForCchanges}\textbf{Table of changes to ForC fields.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
Sites & coordinates.precision & Precision of geographic coordinates, as reported by source or estimated from maps. & field added & allow identification of records with poor coordinate precision\\
\hline
Measuremennts & data.location.within.source & Location of data within the source listed in citation.ID. & field added & facilitate review, ensure traceability\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & Standard deviation, standard error, and lower and upper 95 percent confidence intvervals, respectively. & replaces `stat` and `stat.name` & cleaner format; ability to handle assymetrical 95 percent confidence intervals\\
\hline
 & mean.in.original.units, original.units & mean value and units presented in original publication & fields added & provide IPCC with original units, reduce errors/improve reproducibility\\
\hline
 & C.conversion.factor & Assumed/ measured C content of organic matter used to convert organic matter to C. & field added & track units conversion, allow back-calculation of OM if conversion factor deemed inappropriate\\
\hline
PFT & description & Definition of the pftcode at the community level. Differs from individual level in that properly describes mixed plant functional types. & field added & \\
\hline
 & description.individual & Definition of the pftcode at the individual plant level. & field name change (previously `description`) & \\
\hline
Citations & (several fields) &  &  & \\
\hline
\end{tabu}
\end{table}

>>>>

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Use} & \textbf{Required}\\
\hline
Sites &  &  &  & \\
\hline
Measurements & variable.name & - & link to variable info in ForC\_variables table & y\\
\hline
 & mean & Value & (direct) & y\\
\hline
 & mean.in.original.units & Value in Common Units & (direct) & y\\
\hline
 & original.units & Common Unit & (direct) & y\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI &  &  & y\\
\hline
 &  &  &  & \\
\hline
 & data.location.within.source &  & confirm that data weren't digitized, facilitate finding data in original publication & y\\
\hline
PFT & description &  &  & \\
\hline
variables & units &  &  & y\\
\hline
Citations & (several fields) &  &  & \\
\hline
\end{tabu}
\end{table}

@@

\begin{verbatim}
## 
## -- Column specification --------------------------------------------------------
## cols(
##   Table = col_character(),
##   Column = col_character(),
##   Description = col_character(),
##   Changes = col_character(),
##   Motivation = col_character(),
##   `Date changed` = col_character()
## )
\end{verbatim}

@@

\caption{\label{tab:table_ForCchanges}\textbf{Table of changes to ForC fields.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{Table} & \textbf{Column} & \textbf{Description} & \textbf{Changes} & \textbf{Motivation}\\
\hline
Sites & coordinates.precision & Precision of geographic coordinates, as reported by source or estimated from maps. & field added & allow identification of records with poor coordinate precision\\
\hline
Measurements & data.location.within.source & Location of data within the source listed in citation.ID. & field added & facilitate review, ensure traceability\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI & Standard deviation, standard error, and lower and upper 95 percent confidence intvervals, respectively. & replaces `stat` and `stat.name` & cleaner format; ability to handle assymetrical 95 percent confidence intervals\\
\hline
 & mean.in.original.units, original.units & mean value and units presented in original publication & fields added & provide IPCC with original units, reduce errors/improve reproducibility\\
\hline
 & C.conversion.factor & Assumed/ measured C content of organic matter used to convert organic matter to C. & field added & track units conversion, allow back-calculation of OM if conversion factor deemed inappropriate\\
\hline
PFT & description & Definition of the pftcode at the community level. Differs from individual level in that properly describes mixed plant functional types. & field added & \\
\hline
 & description.individual & Definition of the pftcode at the individual plant level. & field name change (previously `description`) & \\
\hline
Citations & citation.citation & Full citation. Most of these records are automatically generated in R based upon DOI lookup. & field added & field required by IPCC\\
\hline
 & citation.language & Language of original publication, automatically generated based on the title and abstract, with some manual entries and corrections. & field added & field required by IPCC\\
\hline
 & citation.url & URL of original publication, generally retrieved automatically via URL lookup. & field added & field required by IPCC\\
\hline
 & citation.abstract & Abstract, generally retrieved automatically via DOI lookup. & field added & field required by IPCC\\
\hline
 & pdf.in.repository & Indicates whether pdf of original study has been retrieved and saved in ForC's reference repository & field added & housekeeping\\
\hline
\end{tabu}
\end{table}
